---
params: 
  name: "Test name"
  vc: "Terrestrial and Semi-Aquatic SAR"
  a:
    - "Shoreline / Bank stabilization"
    - "Land and Vegetation clearing and vegetation maintenance"
  m:
    - "Relocate"
    - "Create Habitat"
  m_all: 
    - "test"
  notes:
    - "All the notes I think I should include.\nAnd more!"
  lang: 
    - "en"
title: "`r params$vc`"
subtitle: Pathway of Effects
date: today
published-title: "Date"
author: "`r packageVersion('poe')`"
author-title: "poe Tool version"
format: 
  html:
    embed-resources: true
    toc: true
    page-layout: full
    theme: cosmo
keep-md: false
execute:
  echo: false
---

```{css}
/* This is where custom styles are defined */
h4 {
  font-weight: bold;
  font-size: 100%;
  margin-bottom: 0.25rem;
}
```


```{r setup}
#| include: false

# DEVNOTES: Remember to rebuild package before testing!!

library(gt)

list.files("R", full.names = TRUE) |> lapply(source)

vc <- params$vc
a <- params$a
m <- params$m
m_all <- lapply(params$m_all, \(col) {
  col[col == ""] <- NA_character_
  col
})
m_all <- as.data.frame(m_all)

lang <- params$lang

# Load data
pathways <- read_pathways()
ref <- read_components()
```

```{r DEVTESTS}
#| include: false
#| eval: false

# These are used for development tests only, not rendered when creating the report

pathways <- read_pathways()
ref <- read_components()

vc <- "Terrestrial and Semi-Aquatic SAR"
a <- "Shoreline / Bank stabilization"
m <- c("terrestrial_and_semi-aquatic_sar_relocate", "terrestrial_and_semi-aquatic_sar_create_habitat")
m_all <- data.frame(
    start_node = "30",
    end_node = "7",
    short = "Mitigation EG",
    long = "Test"
  )
m_all <- read_mitigations()

m_all <- unique(m_all)
m_all <- lapply(m_all, \(col) {
  col[is.na(col)] <- ""
  col
})
m_all <- lapply(m_all, \(col) {
  col[col == ""] <- NA_character_
  col
})
m_all <- as.data.frame(m_all)
```

This report presents a Pathway of Effects (PoE) diagram modelling the effects of development activities on terrestrial and semi-aquatic species at risk (SAR), including associated mitigation measures. It is based on the user’s selected inputs in the Canadian Wildlife Service (CWS) PoE Shiny R Tool (the `poe` R package), which include the following: 

#### Valued component:
```{r}
#| results: asis
paste("-", paste(vc, collapse = "\n- ")) |> cat()
```

#### Activities:
```{r}
#| results: asis
paste("-", paste(a, collapse = "\n- ")) |> cat()
```

#### Mitigations:
```{r}
#| results: asis
if(length(m) > 0) {
  m_txt <- m_all[[paste0("short_", lang)]][m_all$m_id %in% m] |> unique()
  paste("-", paste(m_txt, collapse = "\n - ")) |> cat()
} else {
  "*None selected*" |> cat()
}
```

To recreate the diagram, the same inputs must be reselected in the tool.

## Notes

```{r notes}
#| results: asis
if(!is.null(params$notes) && params$notes != "") cat(params$notes) else cat("*No user-supplied notes*")
```


## Interactive Diagram
```{r DEVTESTS-diagram}
#| eval: false
# Only used for testing (otherwise eval: false)
write(
  c(
  "vc:", vc, "\n",
  "m:", m, "\n",
  "\n",
  capture.output(print(m_all)), 
  "\n\n",
  capture.output(print(pathways))),
  "~/Projects/Business/CWS/poe/LOG.txt")
```

```{r diagram}
#| fig-height: 10

p <- prep_pathways(pathways, ref, vc = vc, a = a, lang = lang)
d <- add_mitigation(p, m_all, m)
make_visnetwork(d)
```

## Glossary/Details

### Valued Components and Activities

Table of *all* possible Valued Components and their corresponding activities and stressors (not only those in the diagram).
This table can be searched (upper right corner) or individual columns can be filtered (boxes below column name).

```{r tbl_vc_a}
library(reactable)

#TODO: Add translations
tbl <- ref[, c("valued_component", "activities", "stressors")]
tbl <- unique(tbl)
names(tbl) <- stringr::str_replace_all(names(tbl), "_", " ") |>
  stringr::str_to_title()
tbl <- split(tbl, tbl$`Valued Component`)

r <- lapply(
  tbl, 
  \(x) reactable(
    x[, -1], 
    searchable = TRUE, 
    filterable = TRUE
))
```

```{r}
#| include: false
# Required to 'initialize' the reactible (htmltools? htmlwidgets?) printing, even if not seen.
r[[1]]
```

:::{.panel-tabset .nav-pills}

```{r tbl_print}
#| results: asis
for (i in seq_along(r)) {
  cat("###", names(r)[i], "\n\n")
  cat("\n\n```{=html}\n\n")

  shiny::tagList(r[[i]]) |> print()
  
  cat("\n\n```\n\n")
}
```

:::  



```{r tbl_m}
#| results: asis

# Only show mitigations if they have been implemented
if(!is.null(m_all) && length(m_all) > 0) {

  cat("### Mitigations\n\n")

  cat("Table of *all* possible Mitigations for each Valued Component (not only those in the diagram).\n
This table can be searched (upper right corner) or individual columns can be filtered (boxes below column name).")

  tbl <- m_all[, c(paste0("short_", lang), paste0("long_", lang))]
  names(tbl) <- c("Name", "Description") # TODO: Translate
  tbl <- unique(tbl)
  reactable(
    tbl,
    searchable = TRUE,
    filterable = TRUE
  )
}
```

## System information

System information for tracking operating system and software versions used.
Useful for troubleshooting, record keeping, and identifying in which versions
potential bugs may have occurred.

<details>

```{r system_info}
sessionInfo()
```
</details>